---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nationwider

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/nationwider)](https://CRAN.R-project.org/package=nationwider)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/kvasilopoulos/nationwider.svg?branch=master)](https://travis-ci.org/kvasilopoulos/nationwider)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kvasilopoulos/nationwider?branch=master&svg=true)](https://ci.appveyor.com/project/kvasilopoulos/nationwider)
[![Codecov test coverage](https://codecov.io/gh/kvasilopoulos/nationwider/branch/master/graph/badge.svg)](https://codecov.io/gh/kvasilopoulos/nationwider?branch=master)
<!-- badges: end -->

The goal of {nationwider} is to provide house price data from [<nationwide.co.uk>](https://www.nationwide.co.uk/). All datasets available have 
been curated using tidytools and returned in a convenient rectangular tidy format.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/nationwider")
```
## Example

This is a basic example on how to download data with {nationwider}.

```{r example}
library(nationwider)

np <- nationwider::ntwd_get("new_prop")
np
```

We reshape our data from the initial form into a wider form.

```{r wrangling}
library(dplyr)
library(tidyr)

np %>% 
  dplyr::filter(type == "Price") %>% 
  spread(region,value)
```

Here we are plotting all regions using type `Index` and `Price` as facets.

```{r plotting, warning=FALSE}
library(ggplot2)
np %>% 
  ggplot(aes(Date, value, col = region)) +
  geom_line() +
  facet_wrap(~ type, scales = "free")
```

